Elaboration with First-Class Implicit Function Types

### 2020-05-22 paper.tex
revs

\subsubsection{On metatheoretical properties of the core syntax}
We naturally want to make sure that the extended core syntax is still sensible.
In relation to type theories, the following three properties are commonly
considered.
\begin{itemize}
  \item A theory is \emph{consistent} if not every closed type has a closed
    inhabitant. An inconsistent theory cannot be used as a \emph{logic}, from
    the propositions-as-types perspective \cite[Chapter~1]{hottbook}, because
    there every proposition is provable, so proofs do not distinguish truth from
    falsehood.
  \item A theory has the \emph{canonicity} property, if every closed term is
    definitionally equal to a canonical term. For example, every closed natural
    number is a numeral, every $\mathsf{Bool}$ is $\true$ or $\false$ and so
    on. A canonical theory is useful as a \emph{total programming language}; if
    canonicity fails, then some programs compute to stuck terms which cannot be
    viewed as values. In non-total languages, progress and type preservation
    constitute a weaker analogue of canonicity.
  \item A theory has \emph{decidable conversion}, if definitional equality is
    decidable. Undecidable conversion usually implies undecidable type checking
    for type theories. Often, decidable conversion follows from a normalization
    procedure for open terms: we first normalize, then decide equality of normal
    forms.
\end{itemize}

>>>>

\subsubsection{On metatheoretical properties of the core syntax}
We naturally want to make sure that the extended core syntax is still sensible.
In relation to type theories, the following three properties are commonly
considered.
\begin{itemize}
  \item A theory is \emph{consistent} if not every closed type has a closed
    inhabitant. An inconsistent theory cannot be used as a \emph{logic}, from
    the propositions-as-types perspective \cite[Chapter~1]{hottbook}, because
    there every proposition is provable, so proofs do not distinguish truth from
    falsehood.
  \item A theory has the \emph{canonicity} property, if every closed term is
    definitionally equal to a canonical term. For example, every closed natural
    number is a numeral, every $\mathsf{Bool}$ is $\true$ or $\false$ and so
    on. A canonical theory is useful as a \emph{total programming language}; if
    canonicity fails, then some closed programs diverge or compute to stuck
    terms which cannot be viewed as values. In non-total languages, progress and
    type preservation constitute a weaker analogue of canonicity
    \cite[Chapter~6]{harper2016practical}.
  \item A theory has \emph{decidable conversion}, if definitional equality is
    decidable. Undecidable conversion usually implies undecidable type checking
    for type theories. Often, decidable conversion follows from a normalization
    procedure for open terms: we first normalize, then decide equality of normal
    forms.
\end{itemize}
